%-------------------------
% Resume in Latex
% Author : Paolo Torres
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \small 
    \textbf{\Huge \scshape Paolo Torres} \\ \vspace{1pt}
    \href{https://paolo-torres.github.io}{\underline{paolo-torres.github.io}} $|$
    \href{https://www.linkedin.com/in/paolo-torres}{\underline{linkedin.com/in/paolo-torres}} $|$
    \href{https://github.com/paolo-torres}{\underline{github.com/paolo-torres}} $|$ 
    \href{mailto:paolo-torres@hotmail.com}{\underline{paolo-torres@hotmail.com}} $|$ 
    xxx-xxx-xxxx
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Bachelor of Applied Science, Mechatronics Engineering}{Sep. 2016 -- Jun. 2021}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Amazon}{Aug. 2021 -- Present}
      {Software Development Engineer}{Vancouver, BC}

    \resumeSubheading
      {Amazon}{May 2020 -- Aug. 2020}
      {Software Development Engineer Intern}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Developed \textbf{software tools} for 
          \href{https://freight.amazon.com}
          {\underline{Amazon Freight}} 
          to track and monitor the status of shipper invoices}
        \resumeItem{Incorporated sorting, pagination, and filtering of data, deployed to production for \textbf{thousands of users}}
        \resumeItem{Implemented Spring caching to \textbf{improve page load times} from 30s to $<$1s for all subsequent loads}
        \resumeItem{Worked with Java and Spring Framework in the backend, TypeScript and Angular in the frontend}
    \resumeItemListEnd

    \resumeSubheading
      {Clearpath Robotics}{Sep. 2019 -- Dec. 2019}
      {Software Developer Intern}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Implemented firmware with DMX512 and sACN compatibility for control of embedded lighting system}
        \resumeItem{Interfaced with an STM32F407, created device drivers to support UDP transport and SPI conversion}
        \resumeItem{Developed and tested features for \textbf{autonomous ground vehicles} in C++, utilized ROS and CMake}
      \resumeItemListEnd

    \resumeSubheading
      {Microsoft}{Jan. 2019 -- Apr. 2019}
      {Software Engineering Intern}{Redmond, WA}
      \resumeItemListStart
        \resumeItem{Developed \textbf{C++20} 
          \href{https://devblogs.microsoft.com/cppblog/c20-features-and-fixes-in-vs-2019-16-1-through-16-6}
          {\underline{library conformance}} 
          features based on the C++ STL that ships with Visual Studio}
        \resumeItem{Libraries: algorithm, numeric, cmath, containers, type\_traits, string, functional, memory, and new}
        \resumeItem{Optimized function's move constructor to \textbf{reduce object file size} by 30\% for x86 and 45\% for x64}
      \resumeItemListEnd

    \resumeSubheading
      {Microsoft}{May 2018 -- Aug. 2018}
      {Explore Intern}{Redmond, WA}
      \resumeItemListStart
        \resumeItem{Developed Visual Studio 
          \href{https://devblogs.microsoft.com/cppblog/c-productivity-improvements-in-visual-studio-2019-preview-2}
          {\underline{IDE and IntelliSense}} 
          features in C++ and C\#, shipped to \textbf{5 million users}}
        \resumeItem{Added \textbf{telemetry analytics} and full test coverage to track success metrics and increase robustness}
        \resumeItem{Utilized Git and Azure DevOps to track work, participated in sprint meetings, carried out demos}
      \resumeItemListEnd

    \resumeSubheading
      {FLIR Systems}{Sep. 2017 -- Dec. 2017}
      {Robotics Engineering Intern}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Generated fixes on sensors and MCUs to improve temperature reading and flight performance in C}
        \resumeItem{\textbf{Squashed 50+ bugs} in Jira and verified feature requests related to controls, computer vision, and UI}
        \resumeItem{Tested and validated memory management issues, firmware, connectivity, calibration, and custom APIs}
      \resumeItemListEnd

    \resumeSubheading
      {Solink}{Jan. 2017 -- Apr. 2017}
      {Software Developer/QA Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Implemented central data source connector in JavaScript for 10,000+ POS device transactions a day}
        \resumeItem{Wrote camera-based and data extraction automation scripts via REST, \textbf{saving hours of work} a week}
        \resumeItem{Created software tools, patched numerous bugs, and tested the product via Scrum/Agile methodology}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Algorithm Design and Analysis} $|$ \emph{Python, C++}}{Jan. 2021 -- Apr. 2021}
          \resumeItemListStart
            \resumeItem{Built programs with Dijkstra's algorithm and dynamic programming to determine \textbf{shortest paths}}
            \resumeItem{Concepts: Divide-and-conquer, recurrences, greedy, searching/backtracking, approx. algorithms}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Cooperative and Adaptive Algorithms} $|$ \emph{C++, MATLAB}}{Sep. 2020 -- Dec. 2020}
          \resumeItemListStart
            \resumeItem{Utilized genetic algorithms to \textbf{optimize} mathematical expressions and symbolic regression problems}
            \resumeItem{Concepts: Game playing, meta-heuristics, evolutionary computing, swarm intelligence, ant-colony}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Tech}{: Java, JavaScript, HTML/CSS, npm, Node.js, C/C++, C\#, XAML, .NET, Python} \\
     \textbf{Libraries/Frameworks}{: Spring Framework, Angular, C++ STL, libc++, Clang, LLVM, WPF, jQuery} \\
     \textbf{Tools}{: Git, IntelliJ, Terminal, AWS, Visual Studio, Linux, Jira, ROS, CMake, cmd, Azure DevOps} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
